% Copyright (C) 2004-* Jason R. Blevins
% Edit and reproduction - Patrick S. Rhomberg, 2016-2017
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
%
% Edit: the URL was lacking in the .tex I downloaded.

\documentclass[10pt,letterpaper]{article}
\usepackage{textcomp} % \texttildelow
\newcommand\ttt\texttt
\newcommand{\jobEntryTitle}[1]{\item #1}
\newcommand{\jobEntryEntry}[2]{\par\vspace{-.2em}\quad \textit{#1}, #2}
\newcommand{\jobEntry}[3]{\jobEntryTitle{#1}\jobEntryEntry{#2}{#3}}


% Set your name here
\def\name{Dr. Patrick S. Rhomberg}

\usepackage{hyperref}
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {mathematics, computer science, modeling, simulation,
    epidemiology, applied mathematics},
  pdftitle = {\name: R\'esum\'e},
  pdfsubject = {R\'esum\'e},
  pdfpagemode = UseNone
}

\usepackage{geometry}
\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

%%%%%%%%%%%%%%%
%% Begin Doc %%
%%%%%%%%%%%%%%%

\begin{document}

% Place name at left
{\huge \name}
\bigskip

\input{contact_header}
%%%%%%%%%%%%%%%%%%%%

%\section*{Education}
%\begin{itemize}
%  \item Ph.D. Applied Mathematics, The University of Iowa, expected
%    May 2017.
%  \item Master of Computer Science, The University of Iowa, to be awarded
%    Dec. 2016.
%  \item B.A. Mathematics, \textit{Magna Cum Laude}, Wartburg College,
%    2007.
%  \item Budapest Semesters in Mathematics, Spring 2007.
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%


\section*{Work Experience}
\subsection*{Summary}
\begin{itemize}
  \jobEntry{Pivotal Software, Inc.}{Software Engineer}{January 2017 -- present}
  \jobEntry{The University of Iowa, Department of Computer Science}{Teaching Assistant}{September 2014 -- May 2016}
  \jobEntry{Cornell College, Department of Mathematics and Statistics}{Adjunct Professor}{September 30 2013 -- December 12 2013}
  \jobEntryTitle{The University of Iowa, Department of Mathematics}
  \jobEntryEntry{Assistant in Instruction}{September 2013 -- December 2013}
  \jobEntryEntry{Teaching Assistant}{August 2007 -- May 2013}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%

\subsection*{Pivotal Software Inc.}
\textit{Software Engineer}, Jan 2017 -- \verb!$(date +"%b %Y")!
\begin{itemize}
\item Held positions on the Toolsmith, M\&M, and Improved Build teams
\begin{itemize}
\item Toolsmith reponsibilities:
\begin{itemize}
\item Maintain continuous integration pipelines and AWS / GCP infrastructure
\item Provide tools to developes for rapid iteration.
\end{itemize}
\item Monitoring \& Management reponsibilities:
\begin{itemize}
\item Owned user-facing components, such as the command-line tool \verb!gfsh!, configuration APIs, JMX beans.
\item Owned \verb!SecurityManager! interface and enforcement of security throughout the product.
\end{itemize}
\item Improved Build responsibilities:
\begin{itemize}
\item Reduced \verb!precheckin! testing suite execution time from 3 hours to \~45 minutes.
\end{itemize}
\end{itemize}
\end{itemize}

\subsection*{Teaching Highlights}
\begin{itemize}
\item Teaching Assistant for Large Data Analysis (Spring `16)
\item Experience teaching Python (Fall `14 - Fall `15)
\item Adjunct for 4-week, intensive study courses (Cornell, Fall `13)
\item Lecturer for {\em Teaching with Technology} course (Spring `12)
\item Detailed teaching history available at
% TODO: Dead
  \url{cs.uiowa.edu/~prhomber/teaching.pdf}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%

\section*{Fields of Interest}
\begin{itemize}
\item Mathematical Modeling
\item Simulation Modeling
\item Epidemiology
\item Network Diffusion
\item Parallelization
\item Optimization / Operations Research
\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%
\section*{A Summary of Me as a Developer}

\subsection*{Language and Tool proficiencies}
\begin{itemize}
  \item Fluent and well-spoken:
  \begin{itemize}
    \item Java JDK 8
    \item Python (both 2 and 3, with \ttt{python3} preferred) % , including the standard lib, as well as \ttt{numpy}, \ttt{pandas}, \ttt{matplotlib}, et al
    \item The JetBrains family at large, but predominantly IntelliJ and PyCharm, as expected from the above
    \item The Gradle build tool
    \item \ttt{git}, because of course \ttt{git}
    \item Concourse continuous integration
    \item Linux (preference for Xubuntu).  \ttt{emacs} forever.
    \item Concurrency in design and practice, continuous integration
  \end{itemize}
  %
  \item Conversational:
  \begin{itemize}
    \item Java JDK 11, Jigsaw modules
    \item AWS and GCP, predominantly as vehicles for continuous integration testing.
    \item \ttt{vim}, because as much as I prefer \ttt{emacs}, I'm not a zealot and will use the tools available to me.
  \end{itemize}
  %
  \item Out of practice but happy to relearn:
  \begin{itemize}
    \item C / C++, Perl
  \end{itemize}
  %
  \item Neophyte:
  \begin{itemize}
    \item R, Go, Matlab, Gnuplot
  \end{itemize}
\end{itemize}

\subsection*{Strong opinions, loosely held}
\begin{itemize}
  \item A problem does not need to become costly before its solution has value.
  \item A product withers on the vine when its build system is broken.  A responsible developer know how it works.  An excellent developer improves it.
  \item Tests form the contract of permissible product behavior.  Product confidence cannot exist without test confidence.
  \item A responsible developer seeks out the full usefulness of their tools.  (Your IDE can do that for you.  Let it.)
  \item Agile has some good ideas, but it has bad ones, too.  If you're always pivoting, you're not finishing your epics.  Building around individuals isn't scalable.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%

\section*{Research, Presentations, and Academic Interests}
\begin{itemize}
\item Slowly working through the \href{https://projecteuler.net/}{Project Euler} problem sets, since July 2018.
\begin{itemize}
\item Solutions avaialble on GitHub upon request, but private in accordance with the project's wishes.
\end{itemize}
\item
  Doctoral thesis, accepted July 2017:
  \href{https://ir.uiowa.edu/etd/5831/}
    {\em On the Scalable Parallelization of Network Diffusion Models}
\item
    % TODO: dead links
  \href{http://www.math.uiowa.edu/~prhomber/Rhomberg-E3-ModelComparison.pdf}
    {Comparing Agent-Based and Continuous Compartmental Epidemiology Models}
  \begin{itemize}
  \item Epidemics$^3$,
    Boston, MA, November, 2011.
  \end{itemize}
\item
  \href{http://www.math.uiowa.edu/~prhomber/beamer.pdf}
    {Good Looking Mathematics: A Discussion of Mathematical Modeling}
  \begin{itemize}
  \item  Wartburg College, Waverly IA, April, 2013.
  \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%

\subsection*{Current Work}
\begin{itemize}
\item Improving and expanding my Reddit bot \href{
  https://www.reddit.com/user/roll_one_for_me }{
  \ttt{/u/roll\_one\_for\_me}}.
\item Investigating matchmaking strategies for competitive gaming, as approached by network diffusion.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%

\section*{Honors, Awards, and Other Points of Interest}
\begin{itemize}
\item Recipient of The University of Iowa AMCS Summer Research
  Fellowship \par ~ to the maximum allowance of six years: 2007-2012
\item Familiarity with machine learning and neural networks.
\item Familiarity with Django.
\item Experienced using \ttt{git} for version control, \par ~ \ttt{bugs everywhere}
  for issue tracking, \par ~ and \ttt{emacs} for development.
\item Uses Linux (specifically Xubuntu) as primary working environment.
\item Contributor to the Boost Parallel Graph Library.
\item Author of \href{https://www.reddit.com/user/roll_one_for_me}{
  \ttt{/u/roll\_one\_for\_me}}, table-roller for /r/DnDBehindTheScreen and
  related subreddits.
%% \item Diamond Tier in the fighting game Brawlhalla.
%%   \begin{itemize}
%%     \item Season 0: elo rating ~2150, ranked top 100 in US servers.
%%     \item Season 1: peak elo rating 2316, peak ranking 27 on US-East /
%%       72 globally.
%%     \item Season 2: current peak elo rating 2025, peak ranking in top
%%       ~200 globally.
%%   \end{itemize}
\end{itemize}

%\section*{References}
%\begin{itemize}
%\item Dr. Jason Alan Fries 
%?\item Dr. Alberto Segre
%?\item Dr. Brian Birgen
%?\item Amanda
%\end{itemize}

% Footer
\vfill
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}
\end{document}
